---
title: "Week 14 IP Part_1"
author: "Ayub Bett"
date: "2/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#Loading the datatable library
library(data.table)

```

```{r}
#Loading the dataset
carr_1 <- read.csv("http://bit.ly/CarreFourDataset")

#Previewing the top 6 entries
head(carr_1)
```
WE note that we have 16 columns with some categorical variables.

```{r}
#Checking if there null values
colSums(is.na(carr_1))

```


```{r}
#Checking the datatypes of the different variables
str(carr_1)
```

```{r}
#getting unique values of some categorical columns
unique(carr_1$Branch)
unique(carr_1$Customer.type)
unique(carr_1$Gender)
unique(carr_1$Product.line)
unique(carr_1$Payment)
```
###Principal Component Analysis
```{r}
#Since we are working with PCA we will use the numerical columns 
#Choosing the numerical columns
carr_num <- carr_1[,-c(1:5, 9,10,11,13,16)]
head(carr_num)
```


###T-sne 

```{r}
# Loading our tnse library
# 
library(Rtsne)


```

```{r}
# Curating the database for analysis 
# 
target <-carr_1$Total
carr_1$Total<-as.factor(carr_1$Total)

# For plotting
#
colors = rainbow(length(unique(carr_1$Total)))
names(colors) = unique(carr_1$Total)


```

```{r}
# Executing the algorithm on curated data
# 
tsne <- Rtsne(carr_num, dims = 2, perplexity=30, verbose=TRUE, max_iter = 500)

# Getting the duration of execution
# 
exeTimeTsne <- system.time(Rtsne(carr_num, dims = 2, perplexity=30, verbose=TRUE, max_iter = 500))


```

```{r}
# Plotting our graph 
# 
plot(tsne$Y, t='n', main="tsne")
text(tsne$Y, labels=carr_1$Total, col=colors[carr_1$Total])


```
###FEATURE SELECTION
###Using the filter method
```{r}
# Installing and loading our caret package
# ---
# 
suppressWarnings(
        suppressMessages(if
                         (!require(caret, quietly=TRUE))
                install.packages("caret")))
library(caret)
```

```{r}
# Installing and loading the corrplot package for plotting
# ---
# 
suppressWarnings(
        suppressMessages(if
                         (!require(corrplot, quietly=TRUE))
                install.packages("corrplot")))
library(corrplot)

```


```{r}
# Calculating the correlation matrix
# ---
#
corr_Matrix <- cor(carr_num)

# Find attributes that are highly correlated
# ---
corr_Matrix

# Find attributes that are highly correlated
# ---
#Setting our cutoff point to be at 0.5 because its the range of moderate correlation
highly_Corr <- findCorrelation(corr_Matrix, cutoff=0.5)

# Highly correlated attributes
# ---
# 
highly_Corr

names(carr_num[,highly_Corr])
```
We note that the columns with high correlations are Tax, cogs and gross income.


```{r}
# Removing Redundant Features 
# ---
# 
#redundant<-carr_1[-highlyCorrelated]

# Performing our graphical comparison
# ---
# 
par(mfrow = c(1, 2))
corrplot(corr_Matrix, order = "hclust")


```
The correlation heatmap also proves that the three features have a high correlation.
We note that by dropping the three highly correlated features we remain with lesser and workable features.