---
title: "Week_14_IP Part_4"
author: "Ayub Bett"
date: "2/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
library(tidyverse)
library(tibbletime)
library(anomalize)
library(timetk)
library(dplyr)
library(ggplot2)
```

```{r}
#Loading the dataset 
carr_4 <- read.csv("http://bit.ly/CarreFourSalesDataset")

#Previewing the top 6 columns
head(carr_4)


```
```{r}
#Checking the summary of the dataset
summary(carr_4)

#The dataset has 2 columns and 1000 rows

```
```{r}
#Checking if there are null values in the dataset
colSums(is.na(carr_4))

```
There are no null entries in the dataset

```{r}
#Checking the datatypes of the columns
str(carr_4)

```
We note that date column has a datatype of character so we convert to datetime

```{r}
#Converting column into datetime
carr_4$Date <- as.Date(carr_4$Date, format = "%m/%d/%Y")

#Ordering the dates in descending order
carr_4$Date <- sort(carr_4$Date, decreasing = FALSE)
#Checking if the changes have been made
str(carr_4)
```
```{r}
carr_4$Date <- as.POSIXct(carr_4$Date)
```

```{r}
# Converting into tible time
carr_4 <- as_tibble(carr_4)


```

```{r}
#Applying the decompose and recompose function we have
df_anomalized <- carr_4 %>%
    time_decompose(Sales, merge = TRUE) %>%
    anomalize(remainder) %>%
    time_recompose()
df_anomalized %>% glimpse()

```
```{r}
#Plotting to see if there anomalies
df_anomalized %>% plot_anomalies(ncol = 3, alpha_dots = 0.75)
```

From the plot we note that there are anomalies in the dataset, we go further and see if we can find the exact dates the anomalies occurred. We can now find those times when the anomalies ocurred
```{r}
carr_4 %>% 
  time_decompose(Sales) %>%
  anomalize(remainder) %>%
  time_recompose() %>%
  filter(anomaly == 'Yes')

```

We can note that there was an anomaly in sales on date 30th March 2019. So the company should investigate where the problem was.