---
title: "Week 14 IP Part_2"
author: "Ayub Bett"
date: "2/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#library(data.table)
library(arules)
```

```{r}
#loading the dataset
carr_3 <- read.transactions("http://bit.ly/SupermarketDatasetII", sep = ",")

#previewing the top 6 entries
head(carr_3)
```

```{r}
#Verifying the objects class
class(carr_3)
```
Our dataset has been correctly loaded as transaction so we can proceed.

```{r}
#Previewing the first7 items that make up our dataset
items<-as.data.frame(itemLabels(carr_3))
colnames(items) <- "Item"
head(items, 7) 
```
The results above show 7 of the items bought in our dataset. They include almonds, antioxydant juice, asparagus, avocado, babies food, bacon, barbecue sauce.

```{r}
# Previewing our first 3 transactions
#
inspect(carr_3[1:3])
```
```{r}
#Generating a summary of the dataset
summary(carr_3)
```
The summary above give us summary of the dataset showing some of the popular items bought with mineral water leading  the list.
```{r}
# Exploring the frequency of some articles 
# 
itemFrequency(carr_3[, 8:10],type = "absolute")
round(itemFrequency(carr_3[, 8:10],type = "relative")*100,2)

```

```{r}
# Displaying top 10 most common items in the carrefour dataset and the items whose relative importance #is at least 10

par(mfrow = c(1, 2))

# plot the frequency of items
itemFrequencyPlot(carr_3, topN = 10,col="blue")
itemFrequencyPlot(carr_3, support = 0.1,col="hotpink")
```
```{r}
#Setting our rules with parameters set at a support of 0,001 and confidence of 0.8
rules <- apriori (carr_3, parameter = list(supp = 0.001, conf = 0.8))
rules

```
Setting our support at 0.001 and confidence at 0.8 we have 74 rules that can be created from the dataset.  

```{r}
#Inspecting some of the top 5 rules we get the following rules
summary(rules)
inspect(rules[1:5])

```
The following can be derived from the rules above:
1) A person who buys frozen smoothie and spinach has cofidence of 88.89% chance of buying mineral water.
2) Similarly a person who buys bacon and pancakes has a 81.25% chance of buying Spaghetti.

```{r}
#Checking the rules with respect to their confidence in a decreasing manner
rules<-sort(rules, by="confidence", decreasing=TRUE)
inspect(rules[1:5])

```
By looking at the rules with respect to their confidence levels we note that there are some perfect associations with 100 percent likelihood of someone buying the corresponding items such as:
1) A person who buys french fries, mushroomcreamsauce and pasta will eventually buy escalope
2) A customer buying ground beef, light cream and olive oil will eventually buy mineral water.
3) A person buying cake, meatballs and mineral water eventually buys milk 
4) A person who buys cake, olive oil and shrimp will likely buy mineral water.


From our previous revelations about most frequently bought items we can make a promotion of other items oftenly associated with mineral water and eggs.
```{r}
min_water <- subset(rules, subset = rhs %pin% "mineral water")
 
# Then order by confidence
min_water<-sort(min_water, by="confidence", decreasing=TRUE)
inspect(min_water[1:5])

```
The items that can be put closer to mineral water with  a confidence of above 90 percent include ground beef, light cream, olive oil, cake, shrimp, red wine, soup, pancakes, whole wheat rice,frozen vegetables, milk, spaghetti and turkey.

```{r}

#Checking the association of our second most popular item egg
egg <- subset(rules, subset = rhs %pin% "eggs")
 
# Then order by confidence
egg<-sort(egg, by="confidence", decreasing=TRUE)
inspect(egg[1:2])


```
From the results We note that the most common items that can be put close to eggs are black tea, spaghetti, turkey, mineral water, pasta and shrimp.